An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-31 manuscript/Rmd/draft.Rmd
Late night

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  kable(caption = "Descriptive statistics of simulated scores for qualification and final rounds",
        booktabs = TRUE)
```

@@

```{r}
qual %>% 
  rename(Rank = rank) %>% 
  group_by(Rank) %>% 
  summarize(`Average score` = mean(score)) %>% 
  filter(Rank <= 10) %>% 
  kable(caption = "The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.",
        booktabs = TRUE)
```

>>>>

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  kable(caption = "Descriptive statistics of simulated scores for qualification and final rounds",
        booktabs = TRUE,
        position = "H")
```

@@

```{r}
qual %>% 
  rename(Rank = rank) %>% 
  group_by(Rank) %>% 
  summarize(`Average score` = mean(score)) %>% 
  filter(Rank <= 10) %>% 
  kable(caption = "The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.",
        booktabs = TRUE,
        position = "H")
```
